\section{Possible solutions}
\label{sec:possible-solutions}

Since not all challenges are likely to be solved in the first place, a primary task would be the focusing on critical issues to at least boosting the project's overall performance noticeably without losing too much track. This may be worked on in terms of collaboration, as well as in the project's setup, where on the one hand the team's performance and on the one hand the build engine's performance should be improved.

Interestingly, a lot of issues could be covered using GitHub's API, although some project specific adaptions are still necessary. Nevertheless, it provides enough information for quickly perceiving a sufficient overview of the respective repository.

\subsection{Distributed development}
\label{sec:solutions-distributeddevelopment}

Based on GitHub's API and the advantages of using Git as version control system, it could be a significant benefit to equip all project contributors with a GitHub account. While the public, open-source model is free of charge (see ch. \ref{sec:github-history} on p. \pageref{sec:github-history}), there are also different pricing models offered for privately held projects, which should be hidden to the public, starting at 25\$ per month (including 5 user accounts)\footnote{\url{https://github.com/pricing} -- GitHub's pricing models.}.

Although dependent on financial expenditures, the additional value of working on a project with closed source (though it may be released as open source somewhere in the future) may be worth considering. Yet, full-featured access to the API is also included in the free tier though.
