\chapter{Technical foundations}
\label{cha:technicalfoundations}

Before any explanation of the theoretical approach behind this research, there is a need of describing the technical foundations, on which the general thoughts were built on.

Being mostly a back-end web developer since the start of my studies, I experienced a lot of changes in this field. Changes which were mostly caused by the ongoing progression of general web development, but also caused by constantly coming and going ``hypes''. Changes which mostly left minor traces, but sometimes had a major impact on the way I process things during my work on different projects.

\paragraph{EcmaScript 6.}
One of these major turning points was the introduction of EcmaScript 6 (\texttt{ES6}), which I first heard from in a talk given by \emph{Douglas Crockford}\footnote{\url{http://crockford.com} -- Douglas Crockford's website.} in March 2015. He is -- besides other projects -- not only the creator of \texttt{JSLint}\footnote{\url{http://www.jslint.com/help.html} -- JSLint, a code quality tool.}, but also the author of ``\emph{The Good Parts}'' \cite{crockford2008javascript}, a language reference for \texttt{JavaScript}.

\texttt{ES6} introduced a lot of new features, pushing \texttt{JavaScript} more and more towards the definition of an ``object-oriented'' scripting language, thus not only by providing ``real classes'', instead of the old and cumbersome approach of inheritence by setting a constructor function into the \texttt{prototype} object \cite[47]{crockford2008javascript}.

However, the probably most beneficial functions are \texttt{Promises}\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global_Objects/Promise} -- Promise reference on the Mozilla Developer Network.} and \texttt{Arrow functions}\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Functions/Arrow_functions} -- Arrow functions reference on the Mozilla Developer Network.}, both saving significant amounts of code -- especially when working with asynchronous environments, like HTTP requests.

\paragraph{Static site generation.}
Ever since I first got to work with a static site generator, I got more and more interested in how easy and fast static site projects may be scaffolded. Once completely set up, I was simply impressed by its power and variety -- this differed completely from the dynamic web environments I used to work with at that time.

A dynamic web project often demands lots of preparation before receiving any visible outcome, sometimes even when using a predefined framework. Additionally, though many projects in the \texttt{Node.js} universe are already matured to an extent, where they may be even used for enterprise projects, there is still a remaining risk for failing a client due to the amount of dependencies on external services like databases, session storages or user management tools.

\input{chapters/03-technical-foundations/_support/buildpipelines}
\input{chapters/03-technical-foundations/_support/git}
\input{chapters/03-technical-foundations/_support/diff}
