\section{Hexo}
\label{sec:hexo}

\emph{Hexo} understands itself as counterpart to Jekyll, mostly by covering the same ideas of static site generation, but building up completely on Node.js. It even offers a migration service for Octopress- and Jekyll-users who are willing to switch.

\subsection{History}
\label{sec:hexo-history}
\emph{v1.0.0} was originally released in March 2013\footnote{\url{https://github.com/hexojs/hexo/releases/tag/1.0.0} -- Hexo v1.0.0 release page on GitHub.}, although development on GitHub dates back to September 2012 as the first commit was published using the message \emph{``init''}.

\emph{Tommy Chen}, its creator, first used \emph{Octopress}\footnote{\url{http://octopress.org} -- Octopress website.} but quickly became dissatisfied with its performance, as the rendering of 54 blog posts already took more than a minute of compile time \cite{Chen2012hexodebut}. Since he assumed Ruby might be the cause for the lack of performance of his primarily used blogging framework, and further development on this case was not likely to happen any time soon, he decided to look for something which got his attention shortly before: Node.js.

However, Node.js was not really a big player back at that time, so the offer of blogging frameworks written in JavaScript was very dense and not really fitting the needs of Tommy Chen. In his announcement article for Hexo \cite{Chen2012hexodebut}, he references a blog post of \emph{Boris Mann}, also an \texttt{Octopress} user at that time, listing a few Node.js-based blogging frameworks, which were already around in June 2012 \cite{Mann2012nodestaticsite}. Interestingly, only two of all the mentioned ones, \emph{Wintersmith} and \emph{DocPad} are still actively maintained today.

\subsection{Technology}
\label{sec:hexo-technology}
As already stated above, Hexo primarily consists of JavaScript, thus making it easier to start for developers with a front-end web development background. In fact, its GitHub repository shows JavaScript holding a share of 100\% on the source code\footnote{\url{https://github.com/hexojs/hexo} -- Hexo repository on GitHub.}.

\subsubsection{Advantages}
Right from the start, Hexo presents itself using its feature-rich command-line interface (\emph{CLI}), similar to Jekyll. Once it is installed, \texttt{hexo init my\_project} scaffolds a new starter template into the \texttt{./my\_project} folder.\\
As Tommy Chen himself wanted an easy-to-use replacement for Octopress, Jekyll and Hexo share a lot of common features; their content files use both \emph{YAML} frontmatter and \emph{Markdown} by default, even the main configuration file uses a very similar structure in both frameworks. This should make it extremely easy switching from Jekyll to Hexo.

First and foremost, programming-unaware content authors might especially like its CLI, as it also offers to create files based on the \texttt{hexo new} command. Depending on other submitted command-line arguments, Hexo may automatically put the new file in the according sub-folder, whether it is a \emph{draft, page} or \emph{post}. Publishing a draft is as easy as \texttt{hexo publish}.\\
When creating content, Hexo also contains a feature-rich, Octopress-inspired custom tag selection for including content from \emph{YouTube, Vimeo} or \emph{GitHub Gists}.

Additionally, its plugin collection is also constantly growing and mostly community supported. A special naming convention using \texttt{hexo-} as prefix helps by determining which plugins to auto-load out of the \texttt{node\_modules} folder. Using this way, Ruby's \emph{convention over configuration} mantra is ported to JavaScript as well and especially supports beginners by not having to define the usage of a certain plugin.

\subsubsection{Disadvantages}
Hexo might look like as an ideal replacement for Jekyll, but since both share so much similarities, they also share some disadvantages. Whereas Jekyll ships with Liquid and Sass as standard, Hexo does with \emph{EJS} and \emph{Stylus}.\\
Although clearly stated, that both of these plugins might be easily uninstalled later on \cite{HexoDocumentationSetup}, the whole setup pre-installation seems as opinionated as Jekyll's.

In addition to the already mentioned plugin system, a missing configuration option might as well turn out to be misleading in terms of customization options, especially when being dependent on the CLI. If customization is necessary, the developer often is forced to switch to the JavaScript API\footnote{\url{https://hexo.io/api/} -- Hexo's JavaScript API documentation.} or to add a plugin to the project to make the build pipeline fit the customization's needs.

When it comes to caching, Hexo uses a homebrew version of \emph{JSON memory caching} called \emph{Warehouse}, also created by Tommy Chen\footnote{\url{https://github.com/tommy351/warehouse} -- Warehouse repository on GitHub.}, initially mentioned in the release notes of \emph{3.2.0-beta.2} \cite{Chen2015hexorelease}. Using this plugin, a mode called ``Hot processing'' should enable faster rebuilds. The main drawback here might be the caching speed, which is on the one hand filling up the memory when working on bigger projects, whereas the persisting of the database is fully dependent on file input/output write speeds of the underlying hard disk.\\
Furthermore, a constantly growing database file is hardly transferrable when trying to implement a decentralized building system out of Hexo.
